NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-06-27 paper/predSummary.tex
finial edit

By clicking on the treemap node, we can narrow down the selection by focusing on a specific scenario.
As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown. The histogram shows the distribution of the prediction stability in the selected category. For each example, the stability is defined by the ratio of the number of perturbed pairs with the same predicted label and all the perturbed pairs. Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonyms), the stability is 0.8 if 80 of the 100 maintain the original label. 
%The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
%
We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b)).
%
In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), each point corresponds to a sentence pair (the user can focus the rest of the visualization on one particular instance by selection). To help users better assess the \emph{stability} number, we also include the number of perturbed pairs (labeled as \emph{perturbCount}). If the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy and unreliable. %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.

>>>>

By clicking on the treemap node, we can narrow down the selection by focusing on a specific scenario.
As we select the ``E/E'' (ground truth: E-Entailment / predicted label: E-Entailment) category in the treemap (see Fig.~\ref{fig:summaryView}(a)), the histogram (Fig.~\ref{fig:summaryView}(b)) and scatterplot  (Fig.~\ref{fig:summaryView}(c)) are shown. The histogram shows the distribution of the prediction stability in the selected category. For each example, the stability is defined by the ratio of the number of perturbed pairs that maintain the same predicted label and all the perturbed pairs. Assuming we have generated 100 pairs via the automated sentence perturbation operation (i.e., replace nouns and verbs with synonyms), the stability is 0.8 if 80 of the 100 maintain the original label. 
%The \emph{stability} measures how likely a sentence pair will change its prediction after applying minor perturbations.% which helps the expert infer the model stability on the given example.
%
We can further narrow down the focused set by selecting the bins in the histogram (see Fig.~\ref{fig:summaryView}(b)).
%
In the scatterplot (Fig.~\ref{fig:summaryView}(c)(d)), each point corresponds to a sentence pair (the user can focus the rest of the visualization on one particular instance by selection). To help users better assess the \emph{stability} number, we also include the number of perturbed pairs (labeled as \emph{perturbCount}). If the \emph{perturbCount} is rather small ($<10$), then the \emph{stability} value is likely very noisy and unreliable. %For example, if the \emph{perturbCount} is rather small ($<10$), then the \emph{sensitivity} number is likely to be quite noisy and less trustworthy, as compared to the sensitivity ratio computed from a much larger number of perturbed pairs.
